---
title: "Untitled"
author: "Callum Thickett"
date: "25/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(corrplot)
library(caret)
library(gridExtra)
library(scales)
library(Rmisc)
library(ggrepel)
library(randomForest)
library(psych)

```

```{r}
training <- read.csv("train.csv")
test <- read.csv("test.csv")
```

## we will want to combine the 2 data sets for cleaning purposes, first lets look at them individually to see if everything is equal.
```{r}
head(training)
head(test)
```

```{r}
glimpse(training)
glimpse(test)
```

initially, we want to keep all columns except id, we will remove this, keeping the test ids for the submission file
```{r}
test_labels <- test$id
training$Id <-NULL
test$Id <- NULL
```

both have the same number of columns (excluding the response column) and roughly 1460 rows. 
several rows have null values, we will have to clean these 
individually, first we will combine the data sets to make the cleaning process easier. 

```{r}
test$SalePrice <- NA #need same columns to bind
all <- rbind(training,test)
all_fallback <- rbind(training,test)
dim(all)
```

## lets see what columns have null values through a viz.

```{r}
nulcols <-all %>% 
  select(-SalePrice) %>% 
  sapply(.,function(x) sum(is.na(x))) %>% 
  data.frame() %>% 
    rownames_to_column(var="Categories") 
  colnames(nulcols) <- c( "Categories","Count")
  
```


```{r}
nulcols %>% 
  filter(Count > 0) %>% 
  ggplot(aes(x=reorder(Categories,Count),y=Count)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Categories", title="categories that have atleast one null value")
paste("there are",nrow(nulcols %>%filter(Count >0)),"features with atleast one null value.")
```

## look at correlation between features to see if we run into multicolinearity issues and to see what most effects saleprices before anykind of feature engineering/cleaning
```{r}
Numeric_Vars<- which(sapply(all,is.numeric))
Numeric_vars_names <- names(Numeric_Vars)
all_numeric_vars <- all[,Numeric_Vars]
cor_numeric <- cor(all_numeric_vars, use="pairwise.complete.obs")

#want to create matrix and sort by correlation with saleprice

cor_sorted <- as.matrix(sort(cor_numeric[,"SalePrice"],decreasing =TRUE))

## lets just get the values that have a correlation greater than 0.5

cor_high <- names(which(apply(cor_sorted,1,function(x) abs(x) >0.5)))

cor_numeric <- cor_numeric[cor_high,cor_high]

corrplot.mixed(cor_numeric,tl.col="black",tl.pos = "lt",number.cex=0.53)


```

### overallqual and grlivarea are most correlated with saleprice

###can see some areas where multicolinearity will be an issue. mainly with garagecars and garage area which have strong linear correlation with eachother and a similar correlation to SalePrice


### lets look at the most impactful features.

```{r overallqual viz 1}
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(OverallQual),SalePrice))+
  stat_summary(geom ='bar', fun = 'median', fill="blue") +
  geom_label(stat = "count", aes(label=..count.., y=..count..))
  
```

```{r overallqual viz 2}
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(OverallQual),SalePrice)) +
  geom_boxplot()
```

## look at grlivarea

```{r}
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(GrLivArea,SalePrice)) +
  geom_point(col="blue", alpha=0.3) +
  geom_smooth(method = "lm",se=FALSE, formula = y~x, col="black") +
  geom_text_repel(aes(label=ifelse(GrLivArea[!is.na(SalePrice)] >4500,rownames(all),"")))
```

524 and 1299 possible outliers to remove, lets see if the low price is explained by there OverallQual.

```{r}
all[c(524,1299),] %>% 
  select(OverallQual)
```
both have an OverallQual. so yea they may be outliers.


## transforming the data.
###first the numeric columns. we will deal with any null values and transform the data where needed. i.e factor.

```{r}
Numeric_vars_all <- all[,Numeric_vars_names]
paste("there are",ncol(Numeric_vars_all),"numeric columns" )
```
there are 37 numeric columns. we will have to deal with each individually. 

### MSSubClass

```{r MSSubClass}
Numeric_vars_all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(fct_infreq(factor(MSSubClass)),SalePrice)) +
  stat_summary(geom="bar", fun="median", fill="blue") +
  geom_label(stat="count", aes(label=..count..,y=..count..)) 
```

```{r}
sum(is.na(all$MSSubClass))
```
## no null values.

## doesnt seem to be any ordinal properties to MSSubClass so ill just make it a factor.
```{r}
all$MSSubClass <- as.factor(all$MSSubClass)
```

## LotFrontage



```{r}
sum(is.na(all$LotFrontage))
```
## 486 properties with Na lotfrontage, need to give this a value. can find a variable that we could match them to, i.e the median lotfrotange for the neigbourhood theyre in.

```{r}
all %>% 
  filter(!is.na(LotFrontage)) %>% 
  ggplot(aes(Neighborhood,LotFrontage)) +
  stat_summary(geom="bar", fun="median", fill="blue") +
  theme(axis.text.x = element_text(angle = 90)
```


```{r LotFrontage}
for (i in 1:nrow(all)) {
  if(is.na(all$LotFrontage[i])) {
    all$LotFrontage[i] <- as.integer(median(all$LotFrontage[all$Neighborhood ==all$Neighborhood[i]],na.rm = TRUE))
  }
}

```


```{r}
all[!is.na(all$SalePrice),] %>% 
  ggplot(aes(LotFrontage,SalePrice)) +
  geom_point(col="blue",alpha=0.3) +
  geom_smooth(method = "lm", se=FALSE, formula = y~ x,col="black")
```

### take a look at lot area.

```{r LotArea}
sum(all$LotArea[is.na(all$LotArea)])
```
no na values

### lets see how it affects SalePrice

```{r}
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(LotArea,SalePrice)) +
  geom_point() +
  geom_smooth(method="lm", formula = y ~x, se=FALSE) +
  geom_text_repel(aes(label =   ifelse(LotArea>100000,rownames(all),"")))
```
4 data point have a huge LotArea but the saleprice is rather small. no reason to assume these data points are wrong, but we dont want them for modelling purposes. 

lets remove the outliers.

```{r}
all <-all[-c(707,250,336,314),]
  
```

lets see how it affects our lm
```{r}
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(LotArea,SalePrice)) +
  geom_point() +
  geom_smooth(method="lm", formula = y ~x, se=FALSE) +
  geom_text_repel(aes(label =   ifelse(LotArea>100000,rownames(all),"")))
```

it looks so much better!

## OverallQual
```{r OverallQual}
sum(all$OverallQual[is.na(all$OverallQual)])
```
we already look at overallqual. i think its fine as is. (ordinal)

```{r overallCond}
sum(all$OverallCond[is.na(all$OverallCond)])
```

```{r}
#Numeric_vars_names
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(OverallCond),SalePrice)) +
  stat_summary(geom="bar",fun="median") 

```
## i think its ok? again idk if it need to be a factor :(

##YearBuilt
```{r YearBuilt}
sum(all$YearBuilt[is.na(all$YearBuilt)])
```

```{r}
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(YearBuilt,SalePrice)) +
  geom_point() +
  geom_smooth(method="lm", formula = y ~x, se=FALSE) 
```

## YearRemodAdd
```{r YearRemodAdd}
#Numeric_vars_names
sum(all$YearRemodAdd[is.na(all$YearRemodAdd)])
```
interesting part about this one is that if YearRemodAdd ==YearBuilt then it was never remodeled. 

## MasVnrArea
```{r MasVnrArea}
#Numeric_vars_names
sum(all$MasVnrArea[is.na(all$MasVnrArea)])
all$MasVnrArea[is.na(all$MasVnrArea)] <-0
```
some values were NA, changed them to 0. 

### BsmtFinSF1
```{r BsmtFinSF1}
#Numeric_vars_names
which(is.na(all$BsmtFinSF1))
all$BsmtFinSF1[2117]
all$BsmtFinSF1[is.na(all$BsmtFinSF1)] <- 0
```

```{r}
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(BsmtFinSF1,SalePrice)) +
  geom_point()
  
```

```{r BsmtFinSF2}
#Numeric_vars_names
all$BsmtFinSF2[is.na(all$BsmtFinSF2)] <- 0
```

## BsmtUnfSF 
```{r BsmtUnfSF}
all$BsmtUnfSF[is.na(all$BsmtUnfSF)] <- 0
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(BsmtUnfSF,SalePrice)) +
  geom_point()

```
## TotalBsmtSF
```{r TotalBsmtSF}

all$TotalBsmtSF[is.na(all$TotalBsmtSF)] <- 0
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(TotalBsmtSF,SalePrice)) +
  geom_point()
```
## X1stFlrSF

```{r X1stFlrSF}
#Numeric_vars_names
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(X1stFlrSF,SalePrice)) +
  geom_point() +
  geom_smooth(method="lm",se=FALSE, formula =y~x) +
  geom_text_repel(aes(label=ifelse(X1stFlrSF>4000,rownames(all),"")))
```
## may need to deal with row 1299, seem to be an outlier.

## X2ndFlrSF
```{r X2ndFlrSF}
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(X2ndFlrSF,SalePrice)) +
  geom_point() +
  geom_smooth(method="lm",se=FALSE, formula =y~x) +
  geom_text_repel(aes(label=ifelse(X2ndFlrSF>4000,rownames(all),"")))

```

# all the 0 values are throughing off the correlation, maybe we can encode this variable?

## LowQualFinSF
```{r LowQualFinSF}
#Numeric_vars_names
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(LowQualFinSF,SalePrice)) +
  geom_point() +
  geom_smooth(method="lm",se=FALSE, formula =y~x)
```

LowQUALFinSF seems to be a pretty useless variable
## GrLivArea
```{r GrLivArea}
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(GrLivArea,SalePrice)) +
  geom_point() +
  geom_smooth(method="lm",se=FALSE, formula =y~x)

sum(is.na(all$GrLivArea))
```
GrLivArea seems like a good predictor. some values are a bit out there, but probs not an issue (seems like the outliers may cancel out)

## BsmtFullBath
```{r BsmtFullBath}
sum(is.na(all$BsmtFullBath))
##assuming the na values should just be 0 

all$BsmtFullBath[is.na(all$BsmtFullBath)] <- 0

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(BsmtFullBath),SalePrice)) +
  stat_summary(geom="bar", fun="median", fill="blue") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

```
BsmtFullBath needs to be factored, doesnt seem to be ordinal in nature.
```{r}
#Numeric_vars_names

```

##BsmtHalfBath:  

```{r BsmtHalfBath: }
sum(is.na(all$BsmtHalfBath))
all$BsmtHalfBath[is.na(all$BsmtHalfBath)] <- 0 


```
## FullBath

```{r FullBath}
sum(is.na(all$FullBath))

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(FullBath),SalePrice)) +
  stat_summary(geom="bar", fun="median", fill="blue") +
  geom_label(stat="count",aes(label=..count..,y=..count..))


```

## HalfBath
```{r HalfBath}
sum(is.na(all$HalfBath))


```
## BedroomAbvGr

```{r BedroomAbvGr (Bedroom)}
sum(is.na(all$BedroomAbvGr))
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(BedroomAbvGr),SalePrice)) +
  stat_summary(geom="bar",fun="median", fill="blue") +
  geom_label(stat="count",aes(label=..count..,y=..count..))
all$BedroomAbvGr <- as.integer(all$BedroomAbvGr)

```
## Kitchen

```{r Kitchen}

sum(is.na(all$KitchenAbvGr))

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(KitchenAbvGr),SalePrice)) +
  stat_summary(geom="bar",fun="median", fill="blue") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

all$KitchenAbvGr <- as.factor(all$KitchenAbvGr)

```

## KitchenQual

```{r KitchenQual}


>
sum(is.na(all$KitchenQual))

which(is.na(all$KitchenQual))

all[1552,c("KitchenQual","KitchenAbvGr")]

#just set 1552 to be average, i.e TA
all$KitchenQual[1552] <- "TA"

#create quality variable

quality <- c("None"=0,"Po" =1,"Fa"=2,"TA" =3, "Gd" =4, "Ex" =5 ) 
all$KitchenQual <-as.integer(revalue(all$KitchenQual,quality))



all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(KitchenQual),SalePrice)) +
  stat_summary(geom="bar",fun="median", fill="blue") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

```
KitchenQual clearly ordinal data, transformed it accordingly.

##
```{r TotRmsAbvGrd}
sum(is.na(all$TotRmsAbvGrd))

all$TotRmsAbvGrd <- as.integer(all$TotRmsAbvGrd)


```

## Functional
```{r Functional}
sum(is.na(all$Functional))
which(is.na(all$Functional))
all$Functional[c(2470,2213)] <-"Typ"

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(Functional),SalePrice)) +
  stat_summary(geom="bar",fun="median", fill="blue") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

all$Functional <- as.integer(revalue(all$Functional, c("Sal" =0, "Sev" =1, "Maj2" =2,"Maj1"= 3,"Mod"=4,"Min2"=5,"Min1"=6,"Typ"=7)))     
```
## Fireplaces

```{r Fireplaces}

sum(is.na(all$Fireplaces))

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(Fireplaces),SalePrice)) +
  stat_summary(geom="bar",fun="median", fill="blue") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

```

## FireplaceQu

```{r FireplaceQu}

sum(is.na(all$FireplaceQu))

all$FireplaceQu[is.na(all$FireplaceQu)] <-"None"

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(FireplaceQu),SalePrice)) +
  stat_summary(geom="bar",fun="median", fill="blue") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

all$FireplaceQu <- as.integer(revalue(all$FireplaceQu, quality))

```
## GarageType
```{r GarageType}
sum(is.na(all$GarageType))

all$GarageType[is.na(all$GarageType)] <-"None"

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(GarageType,SalePrice)) +
  stat_summary(geom="bar",fun="median", fill="blue") +
  geom_label(stat="count",aes(label=..count..,y=..count..))
## garge type doesnt seem to be ordinal so we shall amke it a factor.

all$GarageType <- as.factor(all$GarageType)

```

## GarageYrBlt

```{r GarageYrBlt}
sum(is.na(all$GarageYrBlt))

all$GarageYrBlt[is.na(all$GarageYrBlt)] <- all$YearBuilt[is.na(all$GarageYrBlt)]

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(GarageYrBlt,SalePrice)) +
  geom_point(col="blue") +
  geom_smooth(method="lm", se=FALSE)


```
since some houses dont have a garage, we cant just remove these rows, or set it to 0. we will just make it equal to the yearbuilt 

## GarageFinish

```{r GarageFinish}
sum(is.na(all$GarageFinish))

## NA values = no garage.
all$GarageFinish[is.na(all$GarageFinish)] <- "None"

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(GarageFinish,SalePrice)) +
  stat_summary(geom="bar",fun="median") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

## clearly ordinal data.

all$GarageFinish <- as.integer(revalue(all$GarageFinish, c("None" = 0,"Unf" =1, "RFn" = 2, "Fin" = 3)))

```
## GarageCars

```{r GarageCars}
sum(is.na(all$GarageCars))
which(is.na(all$GarageCars))

all[2573,c("GarageFinish","GarageType") ]
##seems to be input error, this house doesnt have a garage. ill just set it to 0

all$GarageCars[2573] <- 0

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(GarageCars,SalePrice)) +
  stat_summary(geom="bar",fun="median") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

```


## GarageArea

```{r GarageArea}
sum(is.na(all$GarageArea))
which(is.na(all$GarageArea))
##same house as last time.

all$GarageArea[2573] <- 0

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(GarageArea,SalePrice)) +
  geom_point() +
  geom_smooth(method="lm")

```

```{r}
sum(is.na(all$GarageQual))
##159 Nas corraspond to 0 garages
all$GarageQual[is.na(all$GarageQual)] <-"None"

all$GarageQual <- as.integer(revalue(all$GarageQual,quality))
```

## GarageCond
```{r GarageCond}
all$GarageCond[is.na(all$GarageCond)] <-"None"

all$GarageCond <- as.integer(revalue(all$GarageCond,quality))
```

## PavedDrive

```{r PavedDrive}
sum(is.na(all$PavedDrive))
all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(PavedDrive,SalePrice)) +
  stat_summary(geom="bar",fun="median") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

##clearly ordianl data
all$PavedDrive <- as.integer(revalue(all$PavedDrive, c("N"=0,"P"=1,"Y"=2)))
```



## WoodDeckSF

```{r WoodDeckSF}
sum(is.na(all$WoodDeckSF))

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(WoodDeckSF,SalePrice)) +
  geom_point() +
  geom_smooth(method="lm")
```

## OpenPorchSF: 
```{r OpenPorchSF}
sum(is.na(all$OpenPorchSF))
```

## EnclosedPorch

```{r EnclosedPorch}
sum(is.na(all$EnclosedPorch))
```

## 3SsnPorch

```{r 3SsnPorch}
sum(is.na(all$'3SsnPorch'))
```

## ScreenPorch

```{r ScreenPorch}
sum(is.na(all$ScreenPorch))
```
all porch data looks fine, should probably put these all into one column


# pool data

## PoolArea
```{r PoolArea}
sum(is.na(all$PoolArea))

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(PoolArea,SalePrice)) +
  geom_point() +
  geom_smooth(method="lm")

```

pool area probs not worth using, majority of houses have no pool and it doesnt seem to affect the price too much.
## PoolQC
```{r PoolQC}
sum(is.na(all$PoolQC))

all$PoolQC[is.na(all$PoolQC)] <- "None"

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(PoolQC,SalePrice)) +
  stat_summary(geom="bar", fun="median") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

all$PoolQC <- as.integer(revalue(all$PoolQC,quality))
```

## Fence
```{r Fence}
sum(is.na(all$Fence))

##na values mean no fence.
all$Fence[is.na(all$Fence)] <-"None"

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(Fence,SalePrice)) +
  stat_summary(geom="bar", fun="median") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

## fence seems to have little effect, no clear ordinality so we will just make it a factor
all$Fence <- as.factor(all$Fence)

```

At first glance it looked like this would be ordinal, but doesnt seem to be the case.

## MiscFeature

```{r MiscFeature}
sum(is.na(all$MiscFeature))

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(MiscFeature,SalePrice)) +
  stat_summary(geom="bar", fun="median") +
  geom_label(stat="count",aes(label=..count..,y=..count..))
 #bit pointless, doesnt diviate much and bascilly none of the houses have a tennis court.
```
can probs ignore the MiscFeature data.

## MiscVal

```{r MiscVal}
sum(is.na(all$MiscVal))

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(MiscVal,SalePrice)) +
  geom_point()

```
again, looks like this is a pretty useless feature.

## MoSold

```{r MoSold }
sum(is.na(all$MoSold))

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(MoSold),SalePrice)) +
  stat_summary(geom="bar", fun="median") +
  geom_label(stat="count",aes(label=..count..,y=..c))

## convert to factor
all$MoSold <- as.factor(all$MoSold)

```

## YrSold

```{r YrSold}
sum(is.na(all$YrSold))
summary(all$YrSold)

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(factor(YrSold),SalePrice)) +
  stat_summary(geom="bar", fun="median") +
  geom_label(stat="count",aes(label=..count..,y=..count..))
## convert to factor
all$YrSold <- as.factor(all$YrSold)


```

## SaleType

```{r SaleType}
sum(is.na(all$SaleType))
which(is.na(all$SaleType))

all$SaleType[is.na(all$SaleType)] <-"WD"

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes((SaleType),SalePrice)) +
  stat_summary(geom="bar", fun="median") +
  geom_label(stat="count",aes(label=..count..,y=..count..))

all$SaleType <- as.factor(all$SaleType)

```

## SaleCondition

```{r SaleCondition}

sum(is.na(all$SaleCondition))

all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes((SaleCondition),SalePrice)) +
  stat_summary(geom="bar", fun="median") +
  geom_label(stat="count",aes(label=..count..,y=..count..))
all$SaleCondition <- as.factor(all$SaleCondition)
```

## create another correlation matrix with cleaned variables.

```{r correlation matrix after cleaning}
numeric_vars_clean <- which(sapply(all,is.numeric))
numeric_vars_clean_names <- names(numeric_vars_clean)
numeric_vars_clean_all <- all[,numeric_vars_clean_names]

clean_cor <- cor(numeric_vars_clean_all, use = "pairwise.complete.obs")

clean_sorted <- as.matrix(sort(clean_cor[,"SalePrice"],decreasing=TRUE))

clean_highest <- names(which(apply(clean_sorted,1,function(x) abs(x) >0.5)))
## update clean_cor to have only values that have a correlation of >=0.5 with saleprice.
clean_cor <- clean_cor[clean_highest,clean_highest]
corrplot.mixed(clean_cor, tl.pos = "lt", tl.col="black", t1.cex=0.5, c1.cex=0.5, number.cex=0.45)

```
## feature engineering 


1) sum all bath terms
```{r bath terms}
all <-all %>% 
  mutate(all_baths =((BsmtFullBath) +(BsmtHalfBath*0.5) +(HalfBath*0.5)  +(FullBath)) )

cor(all$all_baths,all$SalePrice)
  
```

2) houses that have been remodeled 

```{r house remodel and age}
## could have just done this in an ifelse statement. 
for (i in 1:nrow(all)) {
  if (all$YearBuilt[i]==all$YearRemodAdd[i]) {
    all[i,"House_Remodeled"] <- 1
  } else {
  all[i,"House_Remodeled"] <- 0
}
}
## house age 
all$age <- as.numeric(levels(all$YrSold))[all$YrSold] - all$YearRemodAdd


all %>% 
  filter(!is.na(SalePrice)) %>% 
  ggplot(aes(age,SalePrice)) +
  geom_point()

cor(all$SalePrice,all$age, use="pairwise.complete.obs")
```

3) consolidating porch sizes

```{r porch size feature}
all$Total_Porch <- all$OpenPorchSF + all$EnclosedPorch + all$X3SsnPorch + all$ScreenPorch

cor(all$SalePrice,all$Total_Porch,use= "pairwise.complete.obs")
```

## bin neigbourhoods and remove correlated variables to avoid multicolinearity.


